---
title: "ST306-Mini Project"
author: "S/18/824"
date: "2024-01-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Load the packages
```{r}
library(tidyverse)
library(janitor)
library(skimr)
library(lubridate)
library(ggplot2)
```

Import the dataset
```{r}
air_quality_data<-read_csv("../data/london_local_data_2022.csv",col_types = c("cfcddddddd"))
head(air_quality_data)
```
```{r}
glimpse(air_quality_data)
```
##In this data set, 10 columns and 289,069 rows are there with some missing values.
##Some monitoring sites in London have nitrite oxides and particulate matter 10 where as in other sites ozone and sulphur dioxide concentration is high.

Handling missing values and NA values
```{r}
air_quality_data <- air_quality_data %>%
  remove_empty(c("cols","rows"))

#view(air_quality_data)
```

##Date is in character format.So,
##Convert date from character to date format
##Using lubridate library
```{r}
air_quality_data$date <- ymd_hms(air_quality_data$date)
str(air_quality_data)
```


```{r}
summary(air_quality_data)
```
##According to this summary statistics we can see concentration of nitrite oxide and ozone is very high in London city.


```{r}
pollutants_1 <- air_quality_data %>%
  filter(!is.na(no2)) %>%
  select(site,code,no2) 
  
head(pollutants_1)
  
```



```{r}
distribution1<-pollutants_1 %>%
  ggplot(mapping = aes(x = as.factor(code),y = no2)) + 
  geom_boxplot() +
  theme_classic()+
  coord_flip() +
  labs(x = "Codes of sites",
       y = "No2",
       title = "No2 concentration in each sites")
distribution1


```
##This graph shows the distribution of No2 in each sites.
##In this data set many outliers are exist.

```{r}
postscript(file = "distribution1.eps",width = 10,height = 5,horizontal = FALSE)
dev.off()
```
```{r}
pollutants_2 <- pollutants_1 %>%
  group_by(code) %>%
  summarise(concentration = sum(no2),Average = mean(no2)) %>%
  arrange(desc(concentration))
pollutants_2
```
##According to this data Lambeth - Brixton Road have high concentration of nitrogen dioxide among 33 monitoring sites.
##Ealing - Hanger Lane Gyratory and City of London - Walbrook Wharf also have high nitrogen dioxide concentration.

```{r}
distribution2 <- pollutants_2 %>%
  ggplot(mapping = aes(x = code, y = concentration)) +
  geom_bar(fill = "red",stat = "identity") +
  coord_flip() +
  labs(x = "codes",
       y = "NO2 concentration",
       title = "No2 concentration with sites") +
  theme_classic()
distribution2

```
##This graph clearly  shows which sites have high No2 concentration.


```{r}
postscript(file = "distribution2.eps",width = 6,height = 4,horizontal = FALSE)
dev.off()
```


```{r}
distribution_3 <- air_quality_data %>%
  group_by(date) %>%
  filter(!is.na(pm2_5),!is.na(pm10)) %>%
  ggplot(mapping = aes(x = date)) +
  geom_line(aes(y = pm10,color = "pm10")) +
  geom_line(aes(y = pm2_5,color = "pm2.5")) +
  labs(x = "Date",
       y = "Particulate Matter level",
       title = "PM10 and PM2.5 levels over time",
       color = "Particle type") 
distribution_3
  
```
##This graph shows the variation of particulate matter 10 and particulate matter 2.5 in each sites in the year 2022.
##Particulate matter 10 is in high amount than that of 2.5 in whole year.
##In the end of November particulate matter 2.5 is in high concentration than particulate matter 2.5 
```{r}
postscript(file = "distribution3.img",width = 6,height = 6,horizontal = FALSE)
dev.off()
```
```{r}
pollutants_3 <- air_quality_data %>%
  filter(!is.na(pm10)) %>%
  group_by(code) %>%
  summarise(count = n(),Average_concentration = mean(pm10))
pollutants_3
```

```{r}
distribution4 <- pollutants_3 %>%
  ggplot(mapping = aes(x = code, y = Average_concentration)) +
  geom_bar(stat = "identity",fill = "blue")
distribution4
```
##According to this graph lambeth has high particulate matter 10 and all other sites have nearly same concentration.

```{r}
pollutants_4 <- air_quality_data %>%
  filter(!is.na(o3)) %>%
  group_by(code) %>%
  summarise(o3_concentration = sum(o3))
pollutants_4

```
##Ozone concentration is measured only in 3 sites and Southwark - Elephant and Castle have high concentration.

```{r}
distribution5 <- pollutants_4 %>%
  group_by(code) %>%
  ggplot(mapping = aes(x = code,y = o3_concentration)) +
  geom_bar(stat = "identity",fill = c("red","green","yellow")) +
  labs(x = "Codes of monitoring sites",
       y = "Ozone concentration",
       title = "Barplot for the ozone concentration in each sites") 
distribution5 
  
```
```{r}
pollutants_4$percent <- scales::percent(pollutants_4$o3_concentration/sum(pollutants_4$o3_concentration))
distribution7 <- pollutants_4 %>%
  group_by(code) %>%
  ggplot(mapping = aes(x = "",y = o3_concentration,fill = code)) +
  geom_bar(stat = "identity",width = 1) +
  coord_polar(theta = "y") +
  theme_void() +
  geom_text(aes(label = percent),position = position_stack(vjust = 0.5))
distribution7
```



```{r}
pm25_by_month <- air_quality_data %>%
  filter(!is.na(pm2_5)) %>%
  mutate(month = format(date,"%m")) %>%
  group_by(month) %>%
  summarise(mean_pm25 = mean(pm2_5))
pm25_by_month
```
```{r}
distribution6 <- pm25_by_month %>%
  ggplot(mapping = aes(x = month, y = mean_pm25)) +
  geom_bar(stat = "identity",fill = "orange") +
  theme_minimal()
distribution6
```
##Check relationship between particulates
```{r}
particulates <- air_quality_data %>%
  filter(!is.na(pm10),!is.na(pm2_5)) %>%
  select(pm10,pm2_5)
particulates

cor(particulates)
```

```{r}
particulates %>%
  ggplot(mapping = aes(x = pm10, y = pm2_5)) +
  geom_point()
```
##There is a strong relationship between two particulates.



